\LARGE{\bf{Natural variation in teosinte at the domestication locus \emph{teosinte branched1} (\emph{tb1})}}\footnotemark

### 2014-07-30 manuscript.tex
edits
discussion

\begin{centering}
\section*{DISCUSSION}
\end{centering}
Adaptation occurs due to selection on standing variation or \emph{de novo} mutations. Adaptation from standing variation has been well-described in a number of systems; for example, selection for lactose tolerance in humans \citep{Plantinga2012, Tishkoff2007}, variation at the \emph{Eda} locus in three-spined stickleback \citep{Kitano2008, Colosimo2005}, and pupal diapause in the Apple Maggot fly \citep{Feder2003}. Although the adaptive role of standing variation has been described in many systems, its importance in domestication is not as well studied.

@@

While gene flow from crops into their wild relatives is well-known, \citep{Ellstrand1999, Zhang2009, Thurber2010, Baack2008, Hubner2012, Wilkes1977, VanHeerwaarden2011, Barrett1983}, our results are more consistent with \citet{Hufford2013} who found resistance to introgression from maize into teosinte around domestication loci. 
We find no evidence of recent introgression in our analyses. Clustering in our NJ trees does not reflect the pattern expected if maize alleles at the \emph{tb1} locus had introgressed into populations of teosinte.  Moreover, there is no signature of elevated LD in the \emph{tb1} region relative to the rest of chromosome 1, and Bayesian assignment to a maize cluster in this region is both low and below the chromosome-wide average (Fig. \ref{Fig3Structure}, Table \ref{Table4Q}). Together, these data point to an explanation other than recent introgression for the high observed frequency of \emph{Hopscotch} in a subset of our \emph{parviglumis} populations.

>>>>

\begin{centering}
\section*{DISCUSSION}
\end{centering}

6) The discussion of introgression, genetic drift, and selection in your Discussion section seems to lack coherence.  It sometimes focuses on explaining the unexpectedly high frequency of Hopscotch in present-day populations, whereas other times it seems to be addressing the presence or absence of Hopscotch in teosinte in general, and it also sometimes seems to be addressing selection on the tb1 locus.

\res{should we restructure this? I thought it read clearly. Key points were 1) Hop more widely spread than previously thought; 2) evidence of selection on Hop in teo}
\jri{clean up, restructure, thank editor, explain changes}

Adaptation occurs due to selection on standing variation or \emph{de novo} mutations. Adaptation from standing variation has been well-described in a number of systems; for example, selection for lactose tolerance in humans \citep{Plantinga2012, Tishkoff2007}, variation at the \emph{Eda} locus in three-spined stickleback \citep{Kitano2008, Colosimo2005}, and pupal diapause in the Apple Maggot fly \citep{Feder2003}. Although the adaptive role of standing variation has been described in many systems, its importance in domestication is not as well studied.

@@

While gene flow from crops into their wild relatives is well-known, \citep{Ellstrand1999, Zhang2009, Thurber2010, Baack2008, Hubner2012, Wilkes1977, VanHeerwaarden2011, Barrett1983}, our results do not suggest introgression from maize into teosinte at the \emph{tb1} locus, and are more consistent with \citet{Hufford2013} who found resistance to introgression from maize into teosinte around domestication loci. 
Clustering in our NJ trees does not reflect the pattern expected if maize alleles at the \emph{tb1} locus had introgressed into populations of teosinte.  Moreover, there is no signature of elevated LD in the \emph{tb1} region relative to the rest of chromosome 1, and Bayesian assignment to a maize cluster in this region is both low and below the chromosome-wide average (Fig. \ref{Fig3Structure}, Table \ref{Table4Q}). Together, these data point to an explanation other than recent introgression for the high observed frequency of \emph{Hopscotch} in a subset of our \emph{parviglumis} populations.
